Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
fixed some oversights in the algorithm
fixed a math typo

\begin{algorithm}[t]
		  \caption{Algorithm to compute  $\rho_t$ for each $t \in  \{\Delta t, 2 \Delta t, \dots, N_t \Delta t$\}.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $\bar{s} > 0$, $N_t \in \mathbb{N}$, $\Delta t > 0$,  $ \{ X_k \}_{k=1}^{n}$, $\hat{x}_0$, $\hat{v}_0$, $\Gamma_L( \hat{x}_0, N_x)$, $\Pr(x_0 \mid M), \Pr(x_0 \mid \hat{x}_0), \Pr(v_0 \mid \hat{v}_0 ), \Pr(M \in \mathcal{M}), \text{ and } \Pr(s \mid k)$.
		    \For {$\ell \in \{1,\dots,N_t\}$}
		    \State Compute $\Phi_{k,1}^{ \pm \bar{s} \ell \Delta t}( x_0^{i,j} )$ for all $x_0^{i,j} \in \Gamma_L( \hat{x}_0 ; N_x)$.
		    \For {$m \in \{-\ell,\dots,\ell\}$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$.
		    \EndFor  
		    \State Compute $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
%		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
		    \hspace*{12pt} with partition $\mathcal{P}_\ell$ of \eqref{eq:partition}.\label{alg1:step2}
		    \State Apply Bayes' Theorem to obtain $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Compute $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$ via \eqref{eq:convolve}.
		    \EndFor
		  \end{algorithmic}
\end{algorithm}

@@

%Steps \ref{alg1:step1} and \ref{alg1:step2} are where the bulk of the work occurs.
%Fortunately, these two steps are embarrassingly parallel and yield tolerable computational complexity for real-time computation.
For fixed $k$, $i$, and $j$, the computation of $\Phi_{k,1}^t(x_0^{i,j})$ at each $t = \{-N_t\bar{s} ,\dots, N_t \bar{s}\}$ takes $\mathcal{O}(N_t)$ time using an explicit finite difference scheme and can be done in parallel for each $k \in \{1,\dots, n\}$ and $x_0^{i,j} \in \Gamma_L( \hat{x}_0; N_x)$.
Similarly, computing $W(k,s,i,j,\hat{x}_0)$ constitutes a series of parallel function evaluations over tuples $(k,s,i,j)$ of the posterior distributions described in \eqref{eq:pgm}, where the continuous variable $s$ is only required at finitely many places in Algorithm \ref{alg:1}.
If the posteriors represented by the arrows in \eqref{eq:pgm} are efficiently computably then the computation of $W(k,s,i,j, \hat{x}_0)$ is equally efficient.
%We summarize this in the following theorem:
%\begin{thm}
%	Suppose we have an accurate scheme for integrating ODEs in a computation time proportional to the integration time-interval\footnote{For example, 4th order explicit Runge-Kutta}.  
%	Algorithm \ref{alg:main} yields an $\mathcal{O}( \Delta x + \bar{s} / \ell + \epsilon_{\rm tol})$ accurate approximation of $\rho_t$ in $\mathcal{O}( N_t n N_x^2 / N_p )$ computation time given $N_p$ processing units and $n$ vector fields.
%\end{thm}

>>>>

\begin{algorithm}[t]
		  \caption{Algorithm to compute  $\rho_t$ for each $t \in  \{\Delta t, 2 \Delta t, \dots, N_t \Delta t$\}.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $\bar{s} > 0$, $N_t \in \mathbb{N}$, $\Delta t > 0$,  $ \{ X_k \}_{k=1}^{n}$, $\hat{x}_0$, $\hat{v}_0$, $\Gamma_L( \hat{x}_0, N_x)$, $\Pr(x_0 \mid M), \Pr(x_0 \mid \hat{x}_0), \Pr(v_0 \mid \hat{v}_0 ), \Pr(M \in \mathcal{M}), \text{ and } \Pr(s \mid k)$.
		    \For {$\ell \in \{1,\dots,N_t\}$}
		    \State Compute $\Phi_{k,1}^{ \pm \bar{s} \ell \Delta t}( x_0^{i,j} )$ for all $x_0^{i,j} \in \Gamma_L( \hat{x}_0 ; N_x)$ and all $k=1,\dots, n$.
		    \For {$m \in \{-\ell,\dots,\ell\}$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$ for all $i,j=-N_x,\dots, N_x$ and $k=1,\dots,n$.
		    \EndFor  
		    \State Compute $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
%		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
		    \hspace*{12pt} with partition $\mathcal{P}_\ell$ of \eqref{eq:partition}.\label{alg1:step2}
		    \State Apply Bayes' Theorem to obtain $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Compute $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$ via \eqref{eq:convolve}.
		    \EndFor
		  \end{algorithmic}
\end{algorithm}

@@

%Steps \ref{alg1:step1} and \ref{alg1:step2} are where the bulk of the work occurs.
%Fortunately, these two steps are embarrassingly parallel and yield tolerable computational complexity for real-time computation.
For fixed $k$, $i$, and $j$, the computation of $\Phi_{k,1}^t(x_0^{i,j})$ at each $t = \{-N_t \Delta t \bar{s} ,\dots, N_t \Delta t \bar{s}\}$ takes $\mathcal{O}(N_t)$ time using an explicit finite difference scheme and can be done in parallel for each $k \in \{1,\dots, n\}$ and $x_0^{i,j} \in \Gamma_L( \hat{x}_0; N_x)$.
Similarly, computing $W(k,s,i,j,\hat{x}_0)$ constitutes a series of parallel function evaluations over tuples $(k,s,i,j)$ of the posterior distributions described in \eqref{eq:pgm}, where the continuous variable $s$ is only required at finitely many places in Algorithm \ref{alg:1}.
If the posteriors represented by the arrows in \eqref{eq:pgm} are efficiently computably then the computation of $W(k,s,i,j, \hat{x}_0)$ is equally efficient.
%We summarize this in the following theorem:
%\begin{thm}
%	Suppose we have an accurate scheme for integrating ODEs in a computation time proportional to the integration time-interval\footnote{For example, 4th order explicit Runge-Kutta}.  
%	Algorithm \ref{alg:main} yields an $\mathcal{O}( \Delta x + \bar{s} / \ell + \epsilon_{\rm tol})$ accurate approximation of $\rho_t$ in $\mathcal{O}( N_t n N_x^2 / N_p )$ computation time given $N_p$ processing units and $n$ vector fields.
%\end{thm}
